Uncovering Distributed System Bugs\\ during Testing (not Production!)

### 2015-08-20 methodology.tex
added some code to explain how the network engine is mocked

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_engine}
\caption{Draft.}
\label{fig:azurestoremodel}
\end{figure}

@@

We now give an example of using dynamic dispatch to model the network engine of an extent manager in the Azure Storage vNext case study. The network engine is responsible for sending to and receiving messages from the various components of the system. During real execution, the network engine uses a custom remote procedure call (RPC) .NET library for communication. For testing, though, it is desirable to replace all calls to this RPC library with \psharp send and receive operations, which can be captured and systematically interleaved to find bugs. We easily achieved this by exposing the original send message operation of the network engine as a virtual method, and then overriding it for testing. In the overridden method, we created a \psharp event and then we wrapped the original message in this event's payload. Then, instead of invoking the RPC library, we invoke the \texttt{PSharpRuntime.Send(...)} method, which asynchronously sends the event (containing the original message) to the target extent node machine.

@@

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/mocked_engine}
\caption{The model machines that replace the real environment during testing of the Extent Manager.}
\label{fig:azurestoremodel}
\end{figure}

@@

We now give an example of using dynamic dispatch to model the network engine of an extent manager in the Azure Storage vNext case study (see Figure~\ref{fig:enginecode}). The network engine is responsible for sending to and receiving messages from the various components of the system. During real execution, the network engine uses a custom remote procedure call (RPC) .NET library for communication. For testing, though, it is desirable to replace all calls to this RPC library with \psharp send and receive operations, which can be captured and systematically interleaved to find bugs. We easily achieved this by exposing the original send message operation of the network engine as a virtual method, and then overriding it for testing. In the overridden method, we created a \psharp event and then we wrapped the original message in this event's payload. Then, instead of invoking the RPC library, we invoke the \texttt{PSharpRuntime.Send(...)} method, which asynchronously sends the event (containing the original message) to the target extent node machine.

@@

\begin{figure}[t]
\begin{lstlisting}
// Public interface of the real network engine
class NetworkEngine {
  public virtual void SendMessage();
  public virtual void EnqueueMessage();
}

// The mocked network engine used during testing
class MockedNetEngine : NetworkEngine {
  ExtentManager EM; // Handle to actual system under test
  MachineId Env; // Handle to modeled environment

  public MockedNetEngine(ExtentManager em, MachineId env) {
    this.EM = em;
    this.Env = env;
  }

  public override void SendMessage(Socket s, Message msg) {
    PSharpRuntime.Send(this.Env, new MsgEvent(), s, msg);
  }

  public override void EnqueueMessage(Message msg) {
    this.EM.ProcessMessage(msg);
  }
}
\end{lstlisting}
\vspace{-2mm}
\caption{The mocked network engine used for testing the Azure Storage vNext system.}
\label{fig:enginecode}
%\vspace{-2mm}
\end{figure}

### 2015-08-20 paper.tex
added some code to explain how the network engine is mocked

\usepackage{url}
\usepackage{xspace}

@@

>>>>

%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{microtype}
%\usepackage{flushend}

\usepackage{url}
\usepackage{listings}
\usepackage{xspace}

@@

\definecolor{bluekeywords}{rgb}{0.13,0.13,1}
\definecolor{greencomments}{rgb}{0,0.5,0}
\definecolor{redstrings}{rgb}{0.9,0,0}

\lstset{language=[Sharp]C,
showspaces=false,
showtabs=false,
breaklines=true,
showstringspaces=false,
breakatwhitespace=true,
escapeinside={(*@}{@*)},
commentstyle=\color{greencomments},
keywordstyle=\color{bluekeywords}\bfseries,
stringstyle=\color{redstrings},
basicstyle=\ttfamily\scriptsize,
columns=fullflexible
}
